The \project{unRAVE} catalog

### 2016-09-08 article/unrave.tex
Updated open cluster figures

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/HRD_OCs.pdf}
\caption{Top panels: Effective temperature $\teff$ and surface gravity $\logg$ from this work for prescribed members of open clusters from \citep{Kunder_2016}.  The same stars are shown for each open cluster in the bottom panels, where the $\teff$ and $\logg$ entries are sourced from the fourth \rave\ data release.\label{fig:open-cluster-HRD}}
\end{figure*}

>>>>

\begin{figure*}[p]
\center
\includegraphics[height=\textheight]{figures/open-clusters.pdf}
\caption{Effective temperature $\teff$ and surface gravity $\logg$ for open cluster members identified by \citep{Kunder_2016}.  Left-hand panels indicate results from the fourth \rave\ data release \citep{Kordopatis_2013}, and the right-hand panels show results from this work.  A representative isochrone is shown for each cluster \citep{Bressan_2012}.\label{fig:open-cluster-HRD}}
\end{figure*}
